Filling in data gaps on refugee children: Statistical imputation for missing count data

### 2023-01-24 paper.qmd
discussion chapter

---
title: "Filling in data gaps on refugee children: Statistical imputation for missing count data"
author: Jan Beise, Yukun Pei (UNICEF); Sebastian Steinmueller (UNHCR)
format: pdf
execute:
  echo: false
  warning: false
  message: false
header-includes:
    \usepackage{float}
    \usepackage{setspace}
    \onehalfspacing
---

@@

UNHCR compiles official statistics on stocks and flows of forcibly displaced and stateless persons twice a year, once for mid-year figures (Mid-Year Statistical Reporting, MYSR) and once for end-year figures (Annual Statistical Reporting, ASR). For these reporting exercises, UNHCR's country offices compile aggregate population figures for refugees and asylum-seekers hosted in their country from a range of sources and data producers such as governments, UNHCR's own refugee registration database proGres and sometimes non-governmental actors. The geographic level on which theses statistics are being produced is therefore always the country country of asylum. The figures undergo a statistical quality control process at the country, regional and global level of the organisation and are disseminated on the publicly available refugee data finder (https://www.unhcr.org/refugee-statistics/) after applying statistical disclosure control to suppress very small counts of persons that could identify individuals. The models and results presented in this paper use data only on the end-year stock of refugees under UNHCR's mandate (including others in need of international protection and refugee-like populations[^1], excluding Palestine refugees under UNRWA's mandate), that is, not on asylum-seekers, internally displaced persons and stateless persons.

@@

```{r, message=FALSE, warning=FALSE}
#| label: tbl-data
#| tbl-cap: UNHCR end-2021 data
#| warning: false
#| error: false
#| echo: false
#| message: false
set.seed(1638)
dem_longMissing %>% 
  filter(total > 1000) %>%
  select(origin_iso3, asylum_iso3, missingAge, female_0_4, female_5_11, male_0_4, male_5_11, total) %>% 
  rename(origin = origin_iso3, asylum = asylum_iso3) %>%
  group_by(missingAge) %>%
  slice_sample(n = 3) %>%
  ungroup %>%
  gt() %>% 
  fmt_number(columns = 4:8, decimals = 0, use_seps = TRUE) %>%
  tab_options(table.font.size = "40%")
```

@@

```{r, message=FALSE, warning=FALSE}
#| label: tbl-missing
#| tbl-cap: UNHCR end-2021 data
#| warning: false
#| error: false
#| echo: false
#| message: false
t.missing %>% 
  gt() %>%
  fmt_number(columns = 2:4, decimals = 0, use_seps = TRUE)
```

@@

When presented with the task of predicting the percentage of children among refugees in a country of asylum A from country of origin B, in the absence of any other information it would intuitively make sense to use the global proportion of children among refugees from that country for whom we have demographic data, i.e. to use data on populations from B from other countries of asylum. We can go further and only use data on refugees from B for countries of asylum in the same geographic region as A, making use of the clustering of proportions seen in @fig-childrenOriAsy. While this procedure works for origins with a sufficient number of countries with available data in all world regions, in some cases we will encounter country pairs with missing data for which there is little or no data available for the same origin in the same region. In these cases, the next best option would be to use the global mean of the proportion of children for that origin country, or, if there is little data even across all countries of asylum, to fall back to the global mean from all origin countries. There are also going to be mix cases, where only data from a low number of countries of asylum in the same region with low population sizes is available. While we do not want to discard such data for the same origin entirely, it would make sense to additionally use data from countries of asylum in other regions for the same origin to avoid relying entirely on little and potentially unreliable data.

@@

For each refugee population $i$ with a total of $n_{i}$ people from country of origin $c$ in country of asylum $a$ in region $r$, we want to predict the vector of counts in the ten age/sex brackets $y_{i} = (y_{1,i},...,y_{k,i},...y_{10,i})$ ($y_{1,i}$ is the count of girls in the 0-4 age bracket, $y_{2,i}$ are girls in the 5-11 bracket, $y_{5,i}$ are women aged 60 and older, $y_{6,i}$ are boys aged 0-4 and so on). $y_{i}$ follows a multinomial distribution: $$y_{i}\sim M(n_{i},\pi_{i})$$ {#eq-multinomial} We fit a multilevel multinomial logit model to estimate from observed age/sex data the vector of probabilities $\pi_{i} = (\pi_{1,i},...,\pi_{k,i},...\pi_{10,i})$ expressing the probability of a refugee falling in age/sex bracket $k$ given their country of origin, country and region of asylum and whether they live in a country neighbouring their origin country: $$log(\frac{\pi_{k,i}}{\pi_{4,i}}) = \eta_{k,i} = \beta_{k,0}+\beta_{k,neighbor}+b_{k,c}+b_{k,r}+b_{k,a}$$ {#eq-linpred} where the counts of the 4th age/sex bracket, women aged 18-59, are the reference category (therefore $\pi_{4,i}$ in the logit denominator). The $\pi_{k}$ sum up to one: $$\sum_{k=1}^{10}\pi_{k,i}=1$$ {#eq-simplex} We use the following priors for the model parameters, where $\Pi_{k}$ is the proportion of the global population in that age/sex group in 2021 (World Population Prospects 2022): $$\beta_{k,0}\sim N(log(\frac{\Pi_{k}}{\Pi_{4}}),1)$$ {#eq-beta0} $$\beta_{k,neighbor}\sim t(7,0,2.5)$$ {#eq-beta1} $$sd(b_{k,c})\sim t(5,0,2.5)$$ {#eq-sdCoO} $$sd(b_{k,r})\sim t(7,0,2.5)$$ {#eq-sdRoA} $$sd(b_{k,a})\sim N(0,0.01)$$ {#eq-sdCoA}

The prior on the global intercepts with the $log(\frac{\Pi_{k}}{\Pi_{4}})$ mean aims to provide sensible levels for the age/sex bracket proportions. It incorporates our prior belief that, for example, it is unlikely that all refugees in a country are girls aged 0 to 4, but otherwise is not overly narrow. The student-t priors on the group-level standard deviations of the intercepts of country of origin and region of asylum are not informative and only serve to regularise the parameter space. The prior on country of origin is slightly wider to allow less pooling (i.e. closer to a separate model for each country of origin) and thereby take into consideration the general idea of the model that age/sex distributions are idiosyncratic to populations of an origin country. The very narrow $N(0,0.01)$ prior on standard deviation of the country of asylum term $b_{k,a}$ merits further discussion: Including the term might seem unusual to start with since in most cases there is only one observation in the form of age/sex counts and total (i.e. one row in the dataset) per country of origin/asylum to start with (exception are countries in Latin America and the Caribbean with two populations displaced from Venezuela, refugees and others in need of international protection). On one hand, leaving out this parameter leads to overconfidence in predicting counts in country pairs with missing data since in that case the counts are drawn from the varying intercepts of the regions (which are observed in the data in most country of origin/region of asylum pairs), ignoring the uncertainty that comes with predicting a whole new country pair not used in fitting the model. On the other hand, allowing a wider standard deviation leads to unreasonably wide prediction intervals (sometimes including counts of zero children in populations of several thousand refugees). Restricting the prior by way of a very small standard deviation helps us constrain the predictive intervals to sensible ranges. We include a fixed effect for neighbouring country pairs since @fig-childrenDist shows that we can on average expect higher proportions of children among refugee populations in neighbouring countries of asylum. Additional covariates such as the distance and GNI difference between country of asylum and origin would be interesting additions to the model, but were left out for this version since they led to too high a number of parameters and numeric instability in the markov chain monte carlo (MCMC) chains.

@@

The model was fit with R-package brms. Reproducible code is available [here](https://github.com/sebastiansteinmueller/ref-demographics-imputation/){.external target="_blank"}. Annex I contains the model summaries.

@@

@tbl-estimates shows the percentage of children among refugees living in the five major world regions estimated with imputations from the model and compares them to the percentage we obtain using the available data only. The global estimate for the proportion of children drops by almost `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenProp) )-as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenMeanProp ) ))` per cent, from `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenProp ) ))` per cent to `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenMeanProp) ))` per cent, when using the imputed dataset. The 95% uncertainty interval for the global point estimate ranges from `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(lowerUI) ),1)` to `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(upperUI) ),1)` per cent and does not include the available-data figure of `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenProp ) ))` per cent. This indicates the standardisation by origins and regions of asylum through the model is relevant, and previously disseminated figures for the proportion of refugees who are children were most likely overestimates. Most of the decrease from the available-data to the modelled estimates is due to the fact that the latter uses data on all refugees residing in Europe and the Americas with lower proportions of children. 
Regional estimates from the imputed data are below the available-data figures with narrow uncertainty intervals for all regions apart from Oceania. The available-data figures in Oceania are based on only `r format(round(as.numeric(  t.dem.asyreg.children |> filter(asylum_region == "Oceania") |>select(total ) ) ), big.mark=",")`` refugees with reported data. The model pools the low estimate from this small dataset towards the global means for each origin, resulting in the comparatively large increase compared toe the available-data estimate.  When interpreting the width of the uncertainty intervals, it is important to keep in mind that only predicted (formerly missing) counts vary over the imputations, but age/sex counts for country pairs with reported data are fixed over the imputations and do therefore not add to uncertainty. This means that regions like Africa with a low proportion of missing data have very few country pairs with imputed data and therefore have narrow uncertainty intervals.

@@

```{r, fig.pos = "H"}
#| label: fig-impChildSyrReg
#| fig-cap: Uncertainty in posterior predictive distribution of the proportion of children among Syrian refugees across regions
#| fig-height: 12.5
#| fig-width: 8
#| warning: false
#| error: false
#| echo: false
#| message: false
p.imputations.syr.reg.children <- ggplot(data = imputations.syr,
    aes(y=reorder(asylum_countryShort, childrenProp), x=childrenProp*100)) +
    stat_pointinterval() +
  labs(x = "Percentage of children") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 13, angle = 0),
      axis.text.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.title.y = element_blank(),
      panel.grid.major.y = element_blank()) +
  facet_wrap(~ asylum_region, scales = "free", ncol = 2) +
  theme(strip.text = element_text(size = 16))

@@

While the imputed dataset is useful in estimating regional and global estimates of the age/sex distribution of refugees, it cannot substitute data collected and compiled for and at the national level. If the main goal is to obtain reliable estimates of the demographic characteristics of refugees on the level of country of asylum, strengthening the production process of official statistics on refugees in said country should be the first order of business. Recommendations and implementation examples developed by countries in the framework of the Expert Group on Refugee, IDP and Statelessness Statistics (EGRISS) can provide helpful guidance to national statistical systems. Projecting populations from census, survey or administrative data with some data and reasonable assumption on fertility, mortality and displacement are another way to obtain more reliable estimates of the age/sex distribution at country level, although they require much more effort for a single country and are therefore better suited if estimates for a specific country are required. Estimates from the imputed dataset at any geographical level should always be disseminated and communicated with uncertainty intervals or by showing the posterior predictive distribution over imputations. The modelling approach is top-down and simply uses geographic proximity and regional groupins as a means to improve available-data figures. Promising improvements would be to use multi-year data and incorporate components of population change to obtain more reliable estimates.

@@

>>>>

---
title: "Filling in data gaps on refugee children: Statistical imputation for missing count data"
author: Jan Beise, Yukun Pei (UNICEF); Sebastian Steinmueller (UNHCR)
abstract: UNHCR's annually published population dataset with the number of refugees and their age/sex composition by country of origin and country of asylum contained missing age data for 23 per cent of the global refugee populations at end-2021. Figures of the global proportion of refugees who are children disseminated to date used the available data only. We show that this approach likely leads to upwards biased estimates of the global proportion of children due to the omission of refugee groups in the Americas and Europe with lower proportions of children. We propose a multilevel Bayesian model to create a dataset with multiple imputations of age/sex counts for country pairs with missing data, resulting in standardisation of global and regional estimates by countries of origin and regions of asylum. The estimate of the proportion of children in the global refugee population derived from the imputed dataset is at 42 per cent compared to 47 per cent in the previously communicated available-data figure. 
format: pdf
bibliography: references.bib
execute:
  echo: false
  warning: false
  message: false
header-includes:
    \usepackage{float}
    \usepackage{setspace}
    \onehalfspacing
toc: true
lof: true
lot: true
---

@@

UNHCR compiles official statistics on stocks and flows of forcibly displaced and stateless persons twice a year, once for mid-year figures (Mid-Year Statistical Reporting, MYSR) and once for end-year figures (Annual Statistical Reporting, ASR). For these reporting exercises, UNHCR's country offices compile aggregate population figures for refugees and asylum-seekers hosted in their country from a range of sources and data producers such as governments, UNHCR's own refugee registration database proGres and sometimes non-governmental actors. The geographic level on which theses statistics are being produced is therefore always the country country of asylum. The figures undergo a statistical quality control process at the country, regional and global level of the organisation and are disseminated on the publicly available refugee data finder [@refdata] after applying statistical disclosure control to suppress very small counts of persons that could identify individuals. The models and results presented in this paper use data only on the end-year stock of refugees under UNHCR's mandate (including others in need of international protection and refugee-like populations[^1], excluding Palestine refugees under UNRWA's mandate), that is, not on asylum-seekers, internally displaced persons and stateless persons.

@@

```{r, message=FALSE, warning=FALSE}
#| label: tbl-data
#| tbl-cap: UNHCR end-2021 data
#| warning: false
#| error: false
#| echo: false
#| message: false
set.seed(1637)
dem_longMissing %>% 
  filter(total > 1000) %>%
  select(origin_iso3, asylum_iso3, missingAge, female_0_4, female_5_11, male_0_4, male_5_11, total) %>% 
  rename(origin = origin_iso3, asylum = asylum_iso3) %>%
  group_by(missingAge) %>%
  slice_sample(n = 3) %>%
  ungroup %>%
  gt() %>% 
  fmt_number(columns = 4:8, decimals = 0, use_seps = TRUE) %>%
  tab_options(table.font.size = "35%")
```

@@

```{r, message=FALSE, warning=FALSE}
#| label: tbl-missing
#| tbl-cap: Missingness of age data
#| warning: false
#| error: false
#| echo: false
#| message: false
t.missing %>% 
  gt() %>%
  fmt_number(columns = 2:4, decimals = 0, use_seps = TRUE)
```

@@

When presented with the task of predicting the percentage of children among refugees in a country of asylum A from country of origin C, in the absence of any other information it would intuitively make sense to use the global proportion of children among refugees from that country for whom we have demographic data, i.e. to use data on populations from C from other countries of asylum. We can go further and only use data on refugees from C for countries of asylum in the same geographic region as A, making use of the clustering of proportions seen in @fig-childrenOriAsy. While this procedure works for origins with a sufficient number of countries with available data in all world regions, in some cases we will encounter country pairs with missing data for which there is little or no data available for the same origin in the same region. In these cases, the next best option would be to use the global mean of the proportion of children for that origin country, or, if there is little data even across all countries of asylum, to fall back to the global mean from all origin countries. There are also going to be mix cases, where only data from a low number of countries of asylum in the same region with low population sizes is available. While we do not want to discard such data for the same origin entirely, it would make sense to additionally use data from countries of asylum in other regions for the same origin to avoid relying entirely on little and potentially unreliable data.

@@

For each refugee population $i$ with a total of $n_{i}$ people from country of origin $c$ in country of asylum $a$ in region $r$, we want to predict the vector of counts in the ten age/sex brackets $y_{i} = (y_{1,i},...,y_{k,i},...y_{10,i})$ ($y_{1,i}$ is the count of girls in the 0-4 age bracket, $y_{2,i}$ are girls in the 5-11 bracket, $y_{5,i}$ are women aged 60 and older, $y_{6,i}$ are boys aged 0-4 and so on). $y_{i}$ follows a multinomial distribution: $$y_{i}\sim M(n_{i},\pi_{i})$$ {#eq-multinomial} We fit a multilevel multinomial logit model to estimate from observed age/sex data the vector of probabilities $\pi_{i} = (\pi_{1,i},...,\pi_{k,i},...\pi_{10,i})$ expressing the probability of a refugee falling in age/sex bracket $k$ given their country of origin, country and region of asylum and whether they live in a country neighbouring their origin country: $$log(\frac{\pi_{k,i}}{\pi_{4,i}}) = \eta_{k,i} = \beta_{k,0}+\beta_{k,neighbor}+b_{k,c}+b_{k,c:r}+b_{k,c:r:a}$$ {#eq-linpred} where the counts of the 4th age/sex bracket, women aged 18-59, are the reference category (therefore $\pi_{4,i}$ in the logit denominator). The subscripts for the varying intercept of region and country of asylum, c:r and c:r:a, indicate nesting within country of origin c (and country of asylum within region of asylum), meaning there are no crossed intercepts of region and country of asylum over countries of origin.  The $\pi_{k}$ sum up to one: $$\sum_{k=1}^{10}\pi_{k,i}=1$$ {#eq-simplex} We use the following priors for the model parameters, where $\Pi_{k}$ is the proportion of the global population in that age/sex group in 2021 (UN DESA 2022): $$\beta_{k,0}\sim N(log(\frac{\Pi_{k}}{\Pi_{4}}),1)$$ {#eq-beta0} $$\beta_{k,neighbor}\sim t(7,0,2.5)$$ {#eq-beta1} $$sd(b_{k,c})\sim t(5,0,2.5)$$ {#eq-sdCoO} $$sd(b_{k,c:r})\sim t(7,0,2.5)$$ {#eq-sdRoA} $$sd(b_{k,c:r:a})\sim N(0,0.01)$$ {#eq-sdCoA}

The prior on the global intercepts with the $log(\frac{\Pi_{k}}{\Pi_{4}})$ mean aims to provide sensible levels for the age/sex bracket proportions. It incorporates our prior belief that, for example, it is unlikely that all refugees in a country are girls aged 0 to 4, but otherwise is not overly narrow. The student-t priors on the group-level standard deviations of the intercepts of country of origin and region of asylum are not informative and only serve to regularise the parameter space. The prior on country of origin is slightly wider to allow less pooling (i.e. closer to a separate model for each country of origin) and thereby take into consideration the general idea of the model that age/sex distributions are idiosyncratic to populations of an origin country. The very narrow $N(0,0.01)$ prior on standard deviation of the country of asylum term $b_{k,a}$ merits further discussion: Including the term might seem unusual to start with since in most cases there is only one observation in the form of age/sex counts and total (i.e. one row in the dataset) per country of origin/asylum to start with (exception are countries in Latin America and the Caribbean with two populations displaced from Venezuela, refugees and others in need of international protection). On one hand, leaving out this parameter leads to overconfidence in predicting counts in country pairs with missing data since in that case the counts are drawn from the varying intercepts of the regions (which are observed in the data in most country of origin/region of asylum pairs), ignoring the uncertainty that comes with predicting a whole new country pair not used in fitting the model. On the other hand, allowing a wider standard deviation leads to unreasonably wide prediction intervals (sometimes including counts of zero children in populations of several thousand refugees). Restricting the prior by way of a very small standard deviation helps us constrain the predictive intervals to sensible ranges. We include a fixed effect for neighbouring country pairs since @fig-childrenDist shows that we can on average expect higher proportions of children among refugee populations in neighbouring countries of asylum. Additional covariates such as the distance and GNI difference between country of asylum and origin would be interesting additions to the model, but were left out for this version since they led to too high a number of parameters and difficulties in convergence of the Markov chains used to sample from the posterior distribution.

@@

The model was fit with R-package brms [@brms]. Reproducible code is available [here](https://github.com/sebastiansteinmueller/ref-demographics-imputation/){.external target="_blank"}. Annex I contains the model summaries.

@@

@tbl-estimates shows the percentage of children among refugees living in the five major world regions estimated with imputations from the model and compares them to the percentage we obtain using the available data only. The global estimate for the proportion of children drops by almost `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenProp) )-as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenMeanProp ) ))` per cent, from `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenProp ) ))` per cent to `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenMeanProp) ))` per cent, when using the imputed dataset. The 95% uncertainty interval for the global point estimate ranges from `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(lowerUI) ),1)` to `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(upperUI) ),1)` per cent and does not include the available-data figure of `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenProp ) ))` per cent. This indicates the standardisation by origins and regions of asylum through the model is relevant, and previously disseminated figures for the proportion of refugees who are children were most likely overestimates. Most of the decrease from the available-data to the modelled estimates is due to the fact that the latter uses data on all refugees residing in Europe and the Americas with lower proportions of children. 
Regional estimates from the imputed data are below the available-data figures with narrow uncertainty intervals for all regions apart from Oceania. The available-data figures in Oceania are based on only 1,209 refugees with reported data. The model pools the low estimate from this small dataset towards the global means for each origin, resulting in the comparatively large increase compared toe the available-data estimate.  When interpreting the width of the uncertainty intervals, it is important to keep in mind that only predicted (formerly missing) counts vary over the imputations, but age/sex counts for country pairs with reported data are fixed over the imputations and do therefore not add to uncertainty. This means that regions like Africa with a low proportion of missing data have very few country pairs with imputed data and therefore have narrow uncertainty intervals.

@@

```{r, fig.pos = "H"}
#| label: fig-impChildSyrReg
#| fig-cap: Uncertainty in posterior predictive distribution of the proportion of children among Syrian refugees across regions
#| fig-height: 12.5
#| fig-width: 8
#| warning: false
#| error: false
#| echo: false
#| message: false
p.imputations.syr.reg.children <- ggplot(data = imputations.syr,
    aes(y=reorder(asylum_countryShort, childrenProp), x=childrenProp*100)) +
    stat_pointinterval() +
  labs(x = "Percentage of children") +
  theme_minimal() +
  theme(axis.text.x = element_text(size = 13, angle = 0),
      axis.text.y = element_blank(),
      axis.title.x = element_text(size = 16),
      axis.title.y = element_blank(),
      panel.grid.major.y = element_blank()) +
  facet_wrap(~ asylum_region, scales = "free", ncol = 2) +
  theme(strip.text = element_text(size = 16),
        panel.spacing = unit(2, "lines"))

@@

While the imputed dataset is useful in estimating regional and global estimates of the age/sex distribution of refugees, the modelling approach is top-down and uses only geographic proximity and regional groupings as a means to improve available-data figures. It cannot substitute data collected and compiled at the national level. If the main goal is to obtain reliable estimates of the demographic characteristics of refugees on the level of country of asylum, strengthening the production process of official statistics on refugees in said country should be the primary course of action. Recommendations and implementation examples developed by countries in the framework of the Expert Group on Refugee, IDP and Statelessness Statistics (see EGRISS 2018) can provide helpful guidance to national statistical systems. Projecting populations from census, survey or administrative data with some data and reasonable assumption on fertility, mortality and displacement are another way to obtain more reliable estimates of the age/sex distribution at country level, although they require much more effort for a single country and are therefore better suited if estimates for a specific country are required. Estimates from the imputed dataset at any geographical level should always be disseminated and communicated with uncertainty intervals or by showing the posterior predictive distribution over imputations. While care has been taken to include and test prior assumptions and hierarchical geographic structures to model uncertainty from parameters and predictions, we made a blanket assumption that all available age/sex data was measured without uncertainty and without measurement error. This is an over-simplification. For example, counts for age/sex brackets on Afghan refugees in Iran reported by UNHCR for end-2021 are outputs of a demographic projection model with its own uncertainty, however these counts are included without variance in the current version of the imputation model. While it would be possible to include estimates of uncertainty for the available part of the age/sex data, this would be technically more challenging and lead to more complex models. It might also be institutionally more difficult since, at least to date, most global datasets such as the one on refugee demographics have been disseminated without measures of uncertainty.

@@

With the revised estimate for the proportion of children among refugees of `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenMeanProp) ),0)` per cent being significantly lower than the available-data figure of `r round(as.numeric( t.worldregion.children |> filter(asylum_region == "WORLD") |>select(childrenProp) ),0)` per cent and in light of the bias in the available data shown in the descriptive analysis, we recommend use of the imputed dataset where the estimation of regional and global figures of age/sex brackets is the goal of an analysis of UNHCR's official refugee data. The imputed dataset is also suitable for analysis on the level of country of asylum or country of origin, however, in these cases particular care should be taken to analyse and communicate the uncertainty over the imputations, for example by disseminating interval- instead of point estimates. The imputed dataset contains iso3 codes for countries of origin and asylum, allowing for straightforward aggregation over custom regions and country groupings as required by an analyst. Since UNHCR's official population dataset have the same format year-on-year, fitting the same model and creating an imputed dataset from its posterior predictive distribution can be repeated for future publications of the ASR data.

While it would seem logical to use the same approach to estimate proportions of children (or other demographic groups) among asylum-seekers and IDPs, the models do not lend themselves naturally to these datasets: The proportion of missing demographic data is much higher among these groups, and the uncertainty in estimating parameters and predicting new values from such sparse datasets would lead to high uncertainty over imputations. For example, age/sex data was only available in 13 out of 35 countries reporting IDPs at end-2021. For IDPs, an additional challenge is the lack of a geographical country of origin/asylum structure as for refugees. Country-by-country demographic projections using additional data such as from censuses and household surveys seem therefore a more promising modelling approach to estimate the age/sex structure for IDPs.

# References
  ---
    nocite: |
      @wpp2022, @irrs
    ...

::: {#refs}
:::
